---
title: "Toronto Saw a Dip in Weddings During Covid"
# subtitle: "My subtitle if needed"
author: 
  - Talia Fabregas
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

marriage_data <- read_csv("/Users/talia/Downloads/STA304Week3/data/analysis_data/marriage_data.csv")

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

We obtained our data from Open Data Toronto. It includes the number of marriages every month at popular city-owned venues in Toronto [@weddingdatasource].

(@fig-marriages1) illustrates how the COVID-19 pandemic impacted the Toronto wedding industry. 

```{r}
#| label: fig-marriages1
#| fig-cap: Number of marriage licenses issued each month in Toronto
#| echo: false
#| warning: false
#| message: false

marriage_data <- read_csv(here::here("data/analysis_data/marriage_data.csv"))
marriage_data |>
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()
```

Talk way more about it. 


# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage


# References


